Sparse Representation Approaches for First Stage Retrieval: A Review

### 2021-11-29 src/article.tex
Update section [Problem formalization]

    For a long time, term-based models were used for the first stage of search, which showed high
    efficiency due to simple logic and the use of an inverse index
    \cite{termBasedModelEfficiency1, termBasedModelEfficiency2}.

@@

>>>>

    For a long time, term-based models were used for the first stage of search, which showed high
    efficiency due to simple logic and the use of an inverse index
    \cite{termBasedModelEfficiency1, termBasedModelEfficiency2}.
    However, this approach has drawbacks in the form of vocabulary mismatch
    \cite{vocabularyMismatch1, vocabularyMismatch2} and lack of consideration of the order of
    terms in documents \cite{ignoringTermOrdering}.
    Thus, term-based models can lose some of the relevant documents at the very beginning.
    To get rid of these limitations, various solutions have been proposed, such as vocabularies
    of synonyms or query \cite{queryExp1,queryExp2,queryExp3,queryExp4} and document
    \cite{docExp1, docExp2, docExp3} expansion.
    However, progress has been limited due to the fact that these approaches still remain in
    the term-based paradigm and inherit its limitations.

    To solve this problem, you can train a neural network that will encode the query and the
    document so that they are in the same semantic space. Most often such spaces are dense
    representations, but they are algorithmically complex because it is necessary to iterate over
    the vectors of documents during the search. In this regard, the researchers decided to
    represent documents and queries in vector spaces of higher dimension (sparse representations)
    with their further application on the inverse index.

@@

    An example is the BM25 \cite{bm25} algorithm which is a retrieval function based on a bag of
    words.
    The scoring function uses TF-IDF weights and term matching at its core in order to
    determine the similarity of a document and a query, with its help at the first stage of
    the search, candidate documents are retrieved for subsequent re-ranking.
